I can see clearly now: reinterpreting statistical significance

### 2018-05-16 doc.tex
Re-drafted intro

\textbf{Abstract}: Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
We believe that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''. commonly uis not about  whatever the use of have led to debates over whether to abandon its use. 
Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g. whether we can clearly see that a correlation or between-group difference is positive or negative).
We therefore suggest that p-values resulting from null-hypothesis tests be described using the language of ``statistical clarity'' rather than ``statistical significance''.
We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.

@@

For nearly a century statisticians and scientists have described the shortcomings of Null Hypothesis Significance Testing
(NHST) \citep[see][]{Cohen1994}. Research articles and books written in the past two decades proposing a deemphasis of the 
p~value in favor of effect sizes and confidence intervals have been cited thousands of times \citep{Cohen1994, Goodman1999, 
Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}. Yet, both reliance on NHST and the misinterpretation of 
results obtained from NHST remain high. In a 2017 meta-analysis of 356 studies published in \emph{European Sociological 
Research}, \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 
49\% interpreted non-significant effects as zero effects, and 44\% failed to report an effect size in a comprehensible 
way. The misuse and misinterpretation of NHST is so pervasive that there has been a recent push for drastically reducing its 
use \citep{SzucsandIoannidis2017} or abandoning its use altogether \citep{McShaneetal.2017}. Others have called for a more
strenuous significance threshold (e.g. $p < 0.005$: \citealt{Benjaminetal.2018}); however, this change is unlikely to reduce
the misuse and misinterpretation of p~values, or the publication bias imposed by any p~value threshold \citep{Ridleyetal.2007}.

Instead, we suggest that using the language of ``statistical clarity'' would help researchers escape the trap of accepting 
the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for
the continued use of NHST as a method of inference (e.g. see \citealt{Abelson1997} for arguments for NHST).

As an example, consider \jd{Should I write a paragraph about signs and clarity?}
The argument for clarity is clearest in the case of What a test of the
null hypothesis actually tells us is whether or not we can \emph{clearly} see our effect. For example, given $H_{0} = 0$ (e.g.
the difference in our treatments is 0) what a $p < 0.05$ tells us is whether or not we can clearly see the sign of the effect.

Therefore, results from NHST (i.e. $p < or > 0.05$) should be described using ``statistical clarity'' instead of ``statistical 
significance''. For example, equating $p < 0.05$ with a zero effect would be much harder to make once a researcher has written 
the following sentence: ``The difference between our control and treatment group was not statistically clear ($p = 0.24$). 
Additionally, the use of larger p~values as increased evidence for the null would be more difficult if the following language
was used: ``We were unable to clearly determine how our control and sham treatments differed''. Finally, in almost all cases 
what a researcher really cares about is the size of an effect and the scientific implications of the effect.  As 
\citet{Bernardietal.2017} state, ``...sociological and social significance are sacrificed on the altar of statistical 
significance''. If ``significant'' were to reclaim its common English definition, conflating $p < 0.05$ with substantive
significance would occur less frequently.

>>>>

\textbf{Abstract}: Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
We believe that a significant \mk{change word?}\jd{I did this on purpose (and also end with ``clarity''). Too cute? I kind of think it could help make the point.} part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.

Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
whether we can clearly see that a correlation or between-group difference is positive or negative).
We therefore suggest that p-values resulting from null-hypothesis tests be described using the language of ``statistical clarity'' rather than ``statistical significance''.
We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.

@@

For nearly a century statisticians and scientists have described the shortcomings of Null Hypothesis Significance Testing (NHST) \citep[see][]{Cohen1994}.

Books and articles proposing a deemphasis of the p~value in favor of effect sizes and confidence intervals have been cited thousands of times \citep{Cohen1994, Goodman1999, Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}.

Yet, both reliance on NHST and the misinterpretation of results obtained from NHST remain high.

In a 2017 meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 
49\% interpreted non-significant effects as zero effects, and 44\% failed to report an effect size in a comprehensible 
way.
The misuse and misinterpretation of NHST is so pervasive that there has been a recent push for drastically reducing 
\citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.

Others have called for a more
strenuous significance threshold (e.g.
$p < 0.005$: \citealt{Benjaminetal.2018}); however, this change is unlikely to reduce
the misuse and misinterpretation of p~values, or the publication bias imposed by any p~value threshold \citep{Ridleyetal.2007}.

Instead, we suggest that using the language of ``statistical clarity'' would help researchers escape the trap of accepting 
the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for
the continued use of NHST as a method of inference (e.g.
see \citealt{Abelson1997} for arguments for NHST).
``Clarity'' is a particularly apt term for what hypothesis tests evaluate. A strong argument in favor or NHST is that testing the null hypothesis (even though we often know that it's false, and can never prove that it's true)  is a proxy for asking whether we can see a difference clearly. In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \cite{robinson2001past}.

Using this language could make sloppy communication and sloppy thinking more difficult. 
For example, we often see sentences like, ``X et al. showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
In fact, the sentence is erroneous even before we get to the implication: X et al.'s significance test provides information about their study, not about the underlying processes \cite{CanWeCiteThis}.
A better formulation would be ``X et al. did not find a significant effect of Y on Z.''
It seems likely, however, that this mistake would be harder to make using the language of clarity:  ``X et al. showed that the effect of Y on Z is unclear'' seems awkward.
Similarly, ``We did not find a clear difference in response between the control and sham groups'' seems both more colloquially accurate and harder to transform into something misleading than ``We did not find a significant difference\ldots''.
\citet{Bernardietal.2017} argued that ``...sociological and social significance are sacrificed on the altar of statistical significance''.
Describing statistical tests in terms of clarity could allow ``significant'' to reclaim its common English definition, and reduce conflation between statistical results and substantive significance.
